A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-30 6_validation.tex
Tim: redo computational results and comparison

\subsubsection{Uniformity}
Depending on the printer hardware configuration, some bead widths might be difficult to produce;
too narrow beads might result in fluttered extrusion and too wide beads might require a pressure in the nozzle beyond the specifications of the machine or they might bulge upward on the sides.
Moreover, bead widths deviating from the preferred bead width by a large amount may be hard to realize and may impact the mechanical properties of the print.
We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.

To evaluate the uniformity of the width,
we calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
We found that the mean width of the inward and evenly distributed schemes is close to preferred bead width of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme. 
These results indicate that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.
We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
The outer beads of the inward distributed scheme deviate less from the preferred width compared to the evenly distributed scheme.

>>>>

\subsubsection{Uniformity}
We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.
We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
We found that the mean width of the inward and evenly distributed schemes is close to preferred bead width of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme. 
These results indicate that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.
We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
The outer beads of the inward distributed scheme deviate less from the preferred width compared to the evenly distributed scheme.

### 2019-08-30 8_discussion.tex
Tim: redo computational results and comparison

However, according to \cref{widthHistogram} the centered scheme exhibits a wider range of bead widths than the distributed schemes:
the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.
We can therefore state that the distributed schemes result in bead widths closer to the preferred widths compared to the centered scheme.
This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.

The inward distributed scheme is introduced with the intention to limit the number of beads deviating from the preferred bead width and to limit the number of angled extrusion segments in transitioning regions.
This expected effect is difficult to be confirmed when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.

However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we can clearly see that the these toolpaths have the preferred bead width more often, which means that errors from inaccuracies due to deviation from the preferred bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all. 
Furthermore, we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}). 
Therefore, when using the inward distributed scheme the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a low percentage.

>>>>

However, according to \cref{widthHistogram} the centered scheme exhibits a wider range of bead widths than the distributed schemes:
the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.
We therefore state that the distributed schemes result in bead widths closer to the preferred widths compared to the centered scheme.
This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.

The inward distributed scheme is introduced with the intention to limit the number of beads deviating from the preferred bead width and to limit the number of angled extrusion segments in transitioning regions.
This expected effect is difficult to be confirmed when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we see that the these toolpaths have the preferred bead width more often, which means that errors from inaccuracies due to deviation from the preferred bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all. 
Furthermore, we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}). 
Therefore, when using the inward distributed scheme the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a low percentage.
